---
title: "Little Blue Stem Wit"
author: "Craig W. Whippo"
date: "December 3, 2020"
output: 
  html_document:
    toc: true
    theme: united
---

```{r Packages, include=FALSE}
library(tidyverse)
library(gt)
library(Beer)

```

```{r message=FALSE, warning=FALSE, include=FALSE}
final_volume <- 5.5
brew_house_efficiency <- 75
pre_boil_volume <- 6 #Gallons
elevation <- 2511 #ft
mash_thickness <- 1.6 #quarts/lb
grain_temp <- 63 #temeperature of the grain
cooler_loss <- 7 #thermal loss of cooler
mash_temp <- 151 #mash temperature
retention_ratio = 0.125 #gallons per pound
step_water <- 0 #gallons
mash_duration <- 60 #minutes
```

```{r Style, echo=FALSE, message=FALSE, warning=FALSE}
Style_Data <- read_csv("Data/2015_Guidelines.csv") 

srm_hex_color <- read_csv("Data/srm_hex_color.csv")

Style_Number <- "24A"	


Selected_Style <- Style_Data %>% 
  filter(Number == Style_Number)


```

# Beer Judge Certification Program Style

> **Style:** `r Selected_Style$Styles`\
> **Number:** `r Selected_Style$Number`\
> **BJCP Category:** `r Selected_Style$"BJCP Categories"`\
> **Style Family:** `r Selected_Style$"Style Family"`\
> **Style Comparison:** `r Selected_Style$"Style Comparison"`\
> **Commercial Examples:** `r Selected_Style$"Commercial Examples"`

## History

> **Origin:** `r Selected_Style$"Origin"`\
> **Style History:** `r Selected_Style$"Style History"`\
> **History:** `r Selected_Style$"History"`

## Sensory

> **Overall Impression:** `r Selected_Style$"Overall Impression"` **Aroma:** `r Selected_Style$"Aroma"` **Appearance:** `r Selected_Style$"Appearance"` **Flavor:** `r Selected_Style$"Flavor"` **Mouthfeel:** `r Selected_Style$"Mouthfell"`

## Ingredients

> **Characteristic Ingredients:** `r Selected_Style$"Characteristic Ingredients"`

## Style Vital Statistics

```{r Vital Stats, echo=FALSE, message=FALSE, warning=FALSE}

Vital_Statistics <- read_csv("Data/StyleData.csv") %>% 
  filter(Number == Style_Number) %>% 
  select(OG_Low, OG_Avg, OG_High, FG_Low,  FG_Avg, FG_High, ABV_Low, ABV_High, ABV_Avg, IBU_Low, IBU_Avg, IBU_High, BU_GU, Relative_Bitterness, SRM_Low, SRM_Avg, SRM_High )

# Extract SRM
SRM_Low <- Vital_Statistics %>% 
  select(SRM_Low)
SRM_High <- Vital_Statistics %>% 
  select(SRM_High)
SRM_Avg <- Vital_Statistics %>% 
  select(SRM_Avg)
SRM_HEX_Low <- srm_hex_color %>% 
  filter(SRM == SRM_Low$SRM_Low)
SRM_HEX_High <- srm_hex_color %>% 
  filter(SRM == SRM_High$SRM_High)
SRM_HEX_Avg <- srm_hex_color %>% 
  filter(SRM == SRM_Avg$SRM_Avg)

gt_table <- gt(data = Vital_Statistics) %>% 
   tab_style(cell_text(align = "left"), cells_title()) %>% 
    tab_source_note(
    source_note = md("Reference: *Beer Judge Certification Program* (2015)")
  ) %>% 
    tab_spanner(
    label = "OG",
    columns = vars(OG_Low, OG_Avg, OG_High)
  ) %>%  
  tab_spanner(
    label = "ABV",
    columns = vars(ABV_Low, ABV_Avg, ABV_High)
  ) %>% 
  tab_spanner(
    label = "IBU",
    columns = vars(IBU_Low, IBU_Avg, IBU_High)
  ) %>% 
  tab_spanner(
    label = "SRM",
    columns = vars(SRM_Low, SRM_Avg, SRM_High)
  ) %>% 
  tab_spanner(
    label = "FG",
    columns = vars(FG_Low, FG_Avg, FG_High)
  ) %>% 
  cols_label(
    ABV_Low = "Min",
    ABV_Avg = "Average",
    ABV_High = "Max",
    IBU_Low = "Min",
    IBU_Avg = "Average",
    IBU_High = "Max",
    SRM_Low = "Min",
    SRM_Avg = "Average",
    SRM_High = "Max",
    OG_Low = "Min",
    OG_Avg = "Average",
    OG_High = "Max",
    FG_Low = "Min",
    FG_Avg = "Average",
    FG_High = "Max",
    BU_GU = "BU:GU",
    Relative_Bitterness = "RBR"
  ) %>% 
    cols_align(
    align = "center"
  ) %>% 
  tab_options(table.align = "left") %>% 
  data_color(
  columns  = vars(SRM_Low),
  colors = SRM_HEX_Low$Code,
  alpha = NULL,
  apply_to = c("fill", "text"),
  autocolor_text = TRUE
)  %>% 
  data_color(
  columns  = vars(SRM_Avg),
  colors = SRM_HEX_Avg$Code,
  alpha = NULL,
  apply_to = c("fill", "text"),
  autocolor_text = TRUE
)%>% 
  data_color(
  columns  = vars(SRM_High),
  colors = SRM_HEX_High$Code,
  alpha = NULL,
  apply_to = c("fill", "text"),
  autocolor_text = TRUE
)

gt_table
```

# Home Brew

## Ingredients

### Grains

```{r Fermentables, include=FALSE}
grain_data <- read_csv("Data/grains.csv")

Fermentables <- tribble(
  ~Grain,                            ~Weight,   ~Cost_per_pound,
  #------------------------------|------------|--------------|
  "Two-Row Okefenokee Pale Malt",  5, 0.65,
  "Rahr White Wheat", 4, 1.35,
  
) %>% left_join(grain_data) %>% 
  mutate(Percent = round(100 * (Weight/sum(Weight)),1)) %>% 
  rename(`Diastic Power (Linter)` = Power) %>% 
  rename(`Weight (lbs)` = Weight) %>%
  mutate(SRM_Avg = round((SRM_Low + SRM_High)/2),2)%>% 
  mutate(Cost = (`Cost_per_pound` *  `Weight (lbs)`)) %>% 
  mutate(Potential = round(Potential, 4))
```

```{r Fermentable Table, echo=FALSE, message=FALSE, warning=FALSE}

Fermentables %>% select(Grain, Manufacturer, Origin, Type, `Must Mash?`, `Weight (lbs)`, Potential, SRM_Avg, `Diastic Power (Linter)`, Cost) %>% 
gt() %>% 
    tab_style(cell_text(align = "left"), cells_title()) %>% 
  tab_options(table.align = "left") %>% 
  cols_align(
    align = "center"
  ) %>% 
    cols_align(
    align = "left",
    columns = vars(Grain, Manufacturer, Origin, Type)
  ) %>% 
  cols_label(
    SRM_Avg = "SRM",
    `Must Mash?` = "Mash") %>% 
  fmt_currency(columns = vars(Cost),
               currency = "USD")
```

### Adjuncts

```{r Adjuncts, echo=FALSE, message=FALSE, warning=FALSE}

adjuncts_data <- read_csv("Data/adjunts.csv") %>% 
    mutate(SRM = `Color` + 0.04662 * (Color)^2) %>% 
  mutate(SRM = round(SRM, 2)) %>% 
  mutate(Potential = 1 + `PPG`/1000)
  
Adjuncts <- tribble(
  ~Adjunct,                       ~Weight,   ~Cost_per_pound,
  #------------------------------|------------|--------------|
  "Oats Flaked",  1.0, 1.89,
  "Rice Hulls", 0.5, 1.57
) %>% left_join(adjuncts_data) %>% 
  mutate(Cost = Weight * Cost_per_pound)



Adjuncts %>% select(Adjunct, Type, `Weight`, Mashing, Potential, SRM, Cost, Description) %>% 
gt()  %>% 
    tab_style(cell_text(align = "left"), cells_title()) %>% 
  tab_options(table.align = "left") %>% 
  fmt_currency(columns = vars(Cost),
               currency = "USD") %>% 
  cols_align(
    align = "center"
  ) %>% 
  cols_label(
    Weight = "Weight (lbs)") %>% 
    cols_align(
    align = "left",
    columns = vars(Adjunct, Type, Description)
  ) 
```

### Specialty Ingredients

```{r Speciality, echo=FALSE, message=FALSE, warning=FALSE}

speciality_data <- read_csv("Data/speciality.csv")

Speciality <- tribble(
  ~Ingredient,          ~Weight,   ~Time,        ~Cost_per_oz,
  #--------------------|------------|---------|---------
  "Coriander",  1, 10, 2.79,
  "Sweet Orange Peel", 1,  10, 3.49,
) %>%  mutate(Cost = Weight * Cost_per_oz) %>% 
  select(-Cost_per_oz)

Speciality %>% 
gt()  %>% 
    tab_style(cell_text(align = "left"), cells_title()) %>% 
  tab_options(table.align = "left") %>% 
  fmt_currency(columns = vars(Cost),
               currency = "USD") %>% 
  cols_align(
    align = "center"
  ) %>% 
  cols_label(
    Weight = "Weight (Oz)",
    Time = "Time (min)") %>% 
  cols_align(
    align = "left",
    columns = vars(Ingredient)
  ) 
```

### Hops

```{r echo=FALSE, message=FALSE, warning=FALSE}

hops_data <- read_csv("Data/hops.csv") %>% 
  mutate(Alpha_Acid_AVG = (Alpha_Acid_LOW + Alpha_Acid_HIGH)/2) %>% 
   mutate(Beta_Acid_AVG = (Beta_Acid_LOW + Beta_Acid_HIGH)/2) %>% 
   mutate(Total_Oil_AVG = (Total_Oil_LOW + Total_Oil_HIGH)/2) %>% 
    mutate(Co_Humulone_AVG = (Co_Humulone_LOW + Co_Humulone_HIGH)/2) %>% 
  mutate(Myrcene_AVG = (Myrcene_LOW + Myrcene_HIGH)/2) %>% 
  mutate(Caryophyllene_AVG = (Caryophyllene_LOW + Caryophyllene_HIGH)/2) %>% 
  mutate(Humulene_AVG = (Humulene_LOW + Humulene_HIGH)/2) 

hops <- tribble(
  ~Variety,   ~Weight,    ~Time,        ~Cost_per_oz,
  #---------|------------|---------|---------
  "Hallertauer Mittelfrüh",  1, 60, 2.49,
) %>%  mutate(Cost = Weight * Cost_per_oz) %>% 
  select(-Cost_per_oz)  %>% 
  left_join(hops_data)



hops %>% select(Variety, Origin, Type, Weight, Time, Alpha_Acid_AVG, Beta_Acid_AVG, Total_Oil_AVG, Co_Humulone_AVG, Myrcene_AVG, Caryophyllene_AVG, Humulene_AVG, Cost) %>%
  gt()  %>% 
  tab_style(cell_text(align = "left"), cells_title()) %>% 
  tab_options(table.align = "left") %>% 
  fmt_currency(columns = vars(Cost),
               currency = "USD") %>% 
  cols_align(
    align = "center"
  ) %>% 
    cols_label(
    Weight = "Weight (Oz)",
    Time = "Time (min)",
    Alpha_Acid_AVG = "Alpha Acid",
    Beta_Acid_AVG = "Beta Acid",
    Total_Oil_AVG = "Total Oil",
    Co_Humulone_AVG = "Co-Humulone (%)",
    Myrcene_AVG = "Myrcene (%)",
    Caryophyllene_AVG = "Caryophyllene (%)",
    Humulene_AVG = "Humulene (%)") %>% 
    cols_align(
    align = "left",
    columns = vars(Variety, Origin, Type)
  ) 





```

### Yeast

```{r Yeast, echo=FALSE, message=FALSE, warning=FALSE}
strain <- "US-05"
yeast_data <- read_csv("Data/yeast.csv") %>% 
  filter(Strain == strain) %>% 
  select(-Substitutions, -`Best Styles`)

yeast_data <- yeast_data %>% select(-Notes) %>% 
  mutate(Attenuation_AVG = (Apparant_Attenuation_Range_LOW + Apparant_Attenuation_Range_HIGH)/2) %>% 
  mutate(Cost = 4.99)

gt(yeast_data) %>% 
  tab_style(cell_text(align = "left"), cells_title()) %>% 
  tab_spanner(
    label = "Temperature",
    columns = vars(Fermentation_Temp_Range_LOW, Fermentation_Temp_Range_HIGH)
  ) %>% 
    tab_spanner(
    label = "Attenuation",
    columns = vars(Apparant_Attenuation_Range_LOW, Attenuation_AVG, Apparant_Attenuation_Range_HIGH)
  )  %>% 
    cols_label(
    Apparant_Attenuation_Range_LOW = "Low",
    Attenuation_AVG = "Average",
    Apparant_Attenuation_Range_HIGH = "High",
    Fermentation_Temp_Range_LOW = "Low",
    Fermentation_Temp_Range_HIGH = "High",
    Alcohol_Tolerance = "Alchohol tolerance (%)"
    ) %>% 
  fmt_currency(columns = vars(Cost),
               currency = "USD") %>% 
  cols_align(
    align = "center")
```

## Recipe Vital Statistics

```{r Recipe Vital Statistics, echo=FALSE, message=FALSE, warning=FALSE}
Attenuation <- yeast_data %>% select(Attenuation_AVG)

Grains <- Fermentables %>% select(`Weight (lbs)`, Potential, SRM_Avg, `Diastic Power (Linter)`) %>%
  rename(Weight = `Weight (lbs)` ) %>% 
  rename(Power =  `Diastic Power (Linter)`) %>% 
  rename(SRM = SRM_Avg) %>% 
  bind_rows(select(Adjuncts, Weight, Potential, SRM)) %>% 
  bind_cols(Attenuation) %>% 
  mutate(Power = replace_na(Power, 0)) %>% 
  mutate(Power = as.numeric(Power))


Vitals <- Grains %>% 
  summarise(
    OG = get_OG(Weight, Potential, brew_house_efficiency, final_volume),
    FG = get_FG(Weight, Potential, brew_house_efficiency, final_volume, Attenuation_AVG),
    ABV = get_ABV(OG, FG),
    SRM = get_SRM(Weight, SRM, final_volume),
    Power = round(get_mash_power(Weight, Power),0)) %>% head(1)



IBUs <- hops %>% 
  summarise(IBU_Tinseth = get_tinseth(Alpha_Acid_AVG/100, Weight, final_volume, Vitals$OG, Time),
            IBU_Rager = get_rager(Alpha_Acid_AVG/100, Weight, final_volume, Vitals$OG, Time),
            IBU_Garetz = get_garetz(Alpha_Acid_AVG/100, Weight, final_volume, Vitals$OG, Time, Vital_Statistics$IBU_Avg, pre_boil_volume, elevation),
            IBU_Daniels = get_daniels(Alpha_Acid_AVG/100, Weight, final_volume, Vitals$OG, Time),
            IBU = round((IBU_Tinseth + IBU_Rager + IBU_Garetz + IBU_Daniels)/4,1))
Vitals <- Vitals %>%  bind_cols(IBUs)

Grain_Costs <- select(Fermentables, Cost) %>% 
          summarise(Cost = sum(Cost)) 
Adjunct_Costs <- select(Adjuncts, Cost) %>% 
          summarise(Cost = sum(Cost)) 
Specialty_Costs <- select(Speciality, Cost) %>% 
          summarise(Cost = sum(Cost)) 
Hop_Costs <- select(hops, Cost) %>% 
          summarise(Cost = sum(Cost)) 
Yeast_Costs <- select(yeast_data, Cost) %>% 
          summarise(Cost = sum(Cost)) 

Total_Costs <- Grain_Costs %>% 
  bind_rows(Adjunct_Costs) %>% 
  bind_rows(Specialty_Costs) %>% 
  bind_rows(Hop_Costs) %>% 
  bind_rows(Yeast_Costs) %>% 
  summarise(Total_Costs = sum(Cost))

Vitals <- Vitals %>%  bind_cols(Total_Costs) %>% 
  mutate(initial_plato = get_plato(OG)) %>% 
  mutate(final_plato = get_plato(FG)) %>% 
  mutate(RE = get_real_extract(initial_plato, final_plato)) %>% 
  mutate(ADF = get_apparent_attenuation(initial_plato, final_plato)) %>% 
  mutate(real_attenuation = get_real_attenuation(RE, initial_plato)) %>% 
  mutate(ABW = get_ABW(ABV, FG)) %>% 
  mutate(calories = get_calories(ABW, RE, FG)) %>% 
  mutate(GU_to_BU = get_BU_to_GU(OG, IBU)) %>% 
  mutate(RBR = get_RBR(GU_to_BU, ADF)) %>% 
  mutate(PG = get_boil_gravity(final_volume, OG, pre_boil_volume)) %>% 
  mutate(final_volume = final_volume) %>% 
  mutate(pre_boil_volume = pre_boil_volume)

SRM_HEX_Reciepe <- srm_hex_color %>% 
  filter(SRM == Vitals$SRM)

Vitals %>% select(SRM, pre_boil_volume, final_volume, PG, OG,  FG, Power, initial_plato, final_plato, RE, ADF, ABV, ABW, calories, IBU, GU_to_BU, RBR, Total_Costs) %>% 
  gt() %>% 
  tab_style(cell_text(align = "left"), cells_title()) %>% 
  fmt_currency(columns = vars(Total_Costs),
               currency = "USD") %>% 
  cols_align(align = "center") %>% 
  fmt_number(
    columns = vars(ADF, GU_to_BU, RBR),
    decimals = 2,
    use_seps = FALSE
  ) %>% 
  fmt_number(
    columns = vars(PG),
    decimals = 3,
    use_seps = FALSE
  ) %>% 
      cols_label(
    initial_plato = "Initial",
    final_plato = "Final",
    calories = "Calories",
    GU_to_BU = "GU:BU",
    Total_Costs = "Total Cost",
    final_volume = "Final",
    pre_boil_volume = "Pre-Boil"
    ) %>% 
    tab_spanner(
    label = "Plato",
    columns = vars(initial_plato, final_plato)) %>% 
    tab_spanner(
    label = "Volume (gallons)",
    columns = vars(final_volume, pre_boil_volume)) %>%
  data_color(
  columns  = vars(SRM),
  colors = SRM_HEX_Reciepe$Code,
  alpha = NULL,
  apply_to = c("fill", "text"),
  autocolor_text = TRUE
) %>%  tab_options(table.align = "left")



```

## Mash Schedule

```{r Mash and Sparge, echo=FALSE, message=FALSE, warning=FALSE}

Mash_Data <- Grains %>% 
  summarise(Grain_Weight = sum(Weight)) %>% 
  mutate(Mash_Thickness = mash_thickness) %>% 
  mutate(Strike_Volume = get_strike_volume(sum(Grains$Weight), mash_thickness)/4) %>% 
  mutate(Grain_Temp = grain_temp) %>% 
  mutate(Mash_temp = mash_temp) %>% 
  mutate(Mash_duration = mash_duration) %>% 
  mutate(Strike_Temp = get_strike_temp(Mash_Thickness, grain_temp, mash_temp, cooler_loss)) %>% 
  mutate(Grain_Absorption = get_grain_absorption(Grain_Weight, retention_ratio)/4) %>% 
  mutate(First_Addition = get_first_running_addition(pre_boil_volume, Grain_Weight, mash_thickness, 0, retention_ratio)) %>% 
  mutate(Second_Addition =  get_second_running_addition(pre_boil_volume)) %>% 
  mutate(Total_Sparge = First_Addition + Second_Addition)
         


    
Mash_Data %>% select(Grain_Weight, Grain_Temp, Mash_duration, Mash_temp, Mash_Thickness, Strike_Volume, Strike_Temp, Grain_Absorption, First_Addition, Second_Addition, Total_Sparge) %>% 
  gt()
    
            
         
        
         
         


```

\#The Boil

## Fermentation

## Priming

## Kegging

# Outcome

## Statistics

## Description

### Appearance
